Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-06 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2, Comment C, part 2

The natural deduction style was chosen for three reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiar with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this.

The first main contribution of this paper is a detailed formalization of Scott's version \citep{scott} of G\"odel's ontological argument \citep{Goedel} (as shown in Section \ref{sec:scott}) in the proposed natural deduction calculus. The second main contribution of the paper is a new proof (also in natural deduction style). In contrast to Scott's proof \citep{scott}, which requires the modal logic \textbf{S5}, the new proof requires only the weaker modal logic \textbf{KB}. The new proof also does not rely on the equality predicate and is much shorter.

>>>>

The natural deduction style was chosen for three reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiar with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicCoq}.

The first main contribution of this paper is a detailed formalization of Scott's version \citep{scott} of G\"odel's ontological argument \citep{Goedel} (as shown in Section \ref{sec:scott}) in the proposed natural deduction calculus. The second main contribution of the paper is a new proof (shown in Section \ref{sec:newproof}), also in natural deduction style. In contrast to Scott's proof \citep{scott}, which requires the modal logic \textbf{S5}, the new proof requires only the weaker modal logic \textbf{KB}. The new proof also does not rely on the equality predicate and is much shorter. Although there have been claims (as discussed in more detail in Section \ref{sec:newproof}) that \textbf{KB} is sufficent and the equality predicate is superfluous, formal proofs substantiating these claims were missing up to now.
